Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-10-27 manuscript/manuscript.Rmd
updates corrections to manuscript and si

Despite the weak climate effects, including climate covariates did increase the accuracy of forecasts for two species: *B. gracilis* and *Poa secunda* (Fig. 2).
However, only for *B. gracilis* were the skill increases statistically significant at $\alpha$ = 0.05 for the IPM ($t_{(279)}$ = 1.70, *P* = 0.045) and the QBM ($t_{(279)}$ = 1.80, *P* = 0.037).
Similarly, forecast error decreased significantly with the inclusion of climate covariates for the *B. gracilis* IPM ($t_{(280)}$ = -3.72, *P* = 0.029) and QBM ($t_{(280)}$ = -3.34, *P* < 0.0001), and for the *Poa secunda* IPM ($t_{(196)}$ = -1.90, *P* < 0.0001) and QBM ($t_{(196)}$ = -2.47, *P* = 0.007) (Fig. S2, Supporting Information).
In no case did including climate covariates significantly decrease forecast skill (Table S21), despite small changes in the mean skill (Fig. 2).

IPM forecasts were significantly more accurate than the QBM in only one case (Fig. 2): forecast accuracy of *P. smithii* percent cover from an IPM with climate covariates was greater than the accuracy from the QBM with climate covariates ($t_{(215)}$ = 1.92, *P* = 0.028).
However, adding climate covariates decreased the skill of both models, and the difference between the IPM and QBM emerges only because skill decreased less for the IPM than the QBM.
Results from all pairwise statistical tests are shown in Table S22 of the Supporting Information.

With climate covariates included and using mean parameter values, the accuracy of both models' forecasts declined as the distance between the last observation and the forecast increased, but they did so at similar rates (Fig. 4).
The only exception is for *Poa secunda*, where QBM forecast accuracy remained steady as the temporal distance of the forecast increased, whereas IPM forecast accuracy declined (Fig. 4).
The forecast horizons were short: forecast accuracy fell below $\rho$ = 0.5 after one year for the IPM for most species, and after four years, at most, for the QBM (Fig. 4).
Across the different temporal distances from the observation to the forecast, the IPM was never more accurate than the QBM (\emph{P} > 0.05 for all one-sided \emph{t}-tests, Table S23).
Likewise, the QBM was rarely more accurate the IPM, the only exception being for \emph{H. comata} at temporal distances of two ($t_{(115)}$ = 2.39, \emph{P} = 0.002) and three years ($t_{(98)}$ = 2.04, \emph{P} = 0.022) (Table S24).
There were some cases where the QBM was more accurate than the IPM for \emph{Poa secunda}, but neither model exceeded the forecast proficiency threshold by a large margin (Fig. 4, Table S24).

>>>>

Despite the weak climate effects, including climate covariates did increase the \textcolor{blue}{mean} accuracy of forecasts for two species: *B. gracilis* and *Poa secunda* (\textcolor{blue}{Fig. S3}).
\textcolor{blue}{However, skill increases were only statistically significant at $\alpha$ = 0.05 for the QBM for \emph{B. gracilis} QBM ($t_{(279)}$ = 1.80, \emph{P} = 0.037).}
Forecast error decreased significantly with the inclusion of climate covariates for the *B. gracilis* IPM ($t_{(280)}$ = -3.72, *P* = \textcolor{blue}{0.01}) and QBM ($t_{(280)}$ = -3.34, *P* < 0.0001), and for the *Poa secunda* IPM ($t_{(196)}$ = -1.90, *P* textcolor{blue}{= 0.015}) and QBM ($t_{(196)}$ = -2.47, *P* = 0.007) (Fig. S1, Supporting Information).
In no case did including climate covariates significantly decrease forecast skill (Table S21), despite small changes in the mean skill (Fig. 2, \textcolor{blue}{Fig. S3}).

IPM forecasts were significantly more accurate than the QBM in only one case (Fig. 2): forecast accuracy of *P. smithii* percent cover from an IPM with climate covariates was greater than the accuracy from the QBM with climate covariates ($t_{(215)}$ = 1.92, *P* = \textcolor{blue}{0.022}).
However, adding climate covariates decreased the skill of both models, and the difference between the IPM and QBM emerges only because skill decreased less for the IPM than the QBM.
Results from all pairwise statistical tests are shown in Table S22 of the Supporting Information.

With climate covariates included and using mean parameter values, the accuracy of both models' forecasts declined as the distance between the last observation and the forecast increased, but they did so at similar rates (Fig. 4).
The only exception is for *Poa secunda*, where QBM forecast accuracy remained steady as the temporal distance of the forecast increased, whereas IPM forecast accuracy declined (Fig. 4).
The forecast horizons were short: forecast accuracy fell below $\rho$ = 0.5 after one year for the IPM for most species, and after four years, at most, for the QBM (Fig. 4).
Across the different temporal distances from the observation to the forecast, the IPM was never more accurate than the QBM (\emph{P} > 0.05 for all one-sided \emph{t}-tests, Table S23).
\textcolor{blue}{Likewise, the QBM was rarely more accurate the IPM, the only exceptions being for \emph{H. comata} at a temporal distance of three years ($t_{(98)}$ = 2.04, \emph{P} = 0.032) and \emph{B. gracilis} at a temporal distance of eight years ($t_{(37)}$ = 1.67, \emph{P} = 0.05) (Table S24).}
\st{There were some cases where the QBM was more accurate than the IPM for \emph{Poa secunda}, but neither model exceeded the forecast proficiency threshold by a large margin (Fig. 4, Table S24).}

### 2016-10-27 manuscript/manuscript.tex
merging
updates corrections to manuscript and si

Despite the weak climate effects, including climate covariates did
increase the accuracy of forecasts for two species: \emph{B. gracilis}
and \emph{Poa secunda} (Fig. 2). However, only for \emph{B. gracilis}
were the skill increases statistically significant at \(\alpha\) = 0.05
for the IPM (\(t_{(279)}\) = 1.70, \emph{P} = 0.045) and the QBM
(\(t_{(279)}\) = 1.80, \emph{P} = 0.037). Similarly, forecast error
decreased significantly with the inclusion of climate covariates for the
\emph{B. gracilis} IPM (\(t_{(280)}\) = -3.72, \emph{P} = 0.029) and QBM
(\(t_{(280)}\) = -3.34, \emph{P} \textless{} 0.0001), and for the
\emph{Poa secunda} IPM (\(t_{(196)}\) = -1.90, \emph{P} \textless{}
0.0001) and QBM (\(t_{(196)}\) = -2.47, \emph{P} = 0.007) (Fig. S2,
Supporting Information). In no case did including climate covariates
significantly decrease forecast skill (Table S21), despite small changes
in the mean skill (Fig. 2).

IPM forecasts were significantly more accurate than the QBM in only one
case (Fig. 2): forecast accuracy of \emph{P. smithii} percent cover from
an IPM with climate covariates was greater than the accuracy from the
QBM with climate covariates (\(t_{(215)}\) = 1.92, \emph{P} = 0.028).
However, adding climate covariates decreased the skill of both models,
and the difference between the IPM and QBM emerges only because skill
decreased less for the IPM than the QBM. Results from all pairwise
statistical tests are shown in Table S22 of the Supporting Information.

With climate covariates included and using mean parameter values, the
accuracy of both models' forecasts declined as the distance between the
last observation and the forecast increased, but they did so at similar
rates (Fig. 4). The only exception is for \emph{Poa secunda}, where QBM
forecast accuracy remained steady as the temporal distance of the
forecast increased, whereas IPM forecast accuracy declined (Fig. 4). The
forecast horizons were short: forecast accuracy fell below \(\rho\) =
0.5 after one year for the IPM for most species, and after four years,
at most, for the QBM (Fig. 4). Across the different temporal distances
from the observation to the forecast, the IPM was never more accurate
than the QBM (\emph{P} \textgreater{} 0.05 for all one-sided
\emph{t}-tests, Table S23). Likewise, the QBM was rarely more accurate
the IPM, the only exception being for \emph{H. comata} at temporal
distances of two (\(t_{(115)}\) = 2.39, \emph{P} = 0.002) and three
years (\(t_{(98)}\) = 2.04, \emph{P} = 0.022) (Table S24). There were
some cases where the QBM was more accurate than the IPM for
\emph{Poa secunda}, but neither model exceeded the forecast proficiency
threshold by a large margin (Fig. 4, Table S24).

@@

\subsection{References}\label{references}
\addcontentsline{toc}{subsection}{References}

@@

\subsection{Supporting Information}\label{si}
\begin{description}
  \item[Appendix S1.] Detailed methods and Stan code examples for the vital rate and percent cover regressions; Figures S1 and S2; Tables S1-S24.
\end{description

>>>>

Despite the weak climate effects, including climate covariates did
increase the \textcolor{blue}{mean} accuracy of forecasts for two
species: \emph{B. gracilis} and \emph{Poa secunda}
(\textcolor{blue}{Fig. S3}).
\textcolor{blue}{However, skill increases were only statistically significant at $\alpha$ = 0.05 for the QBM for \emph{B. gracilis} QBM ($t_{(279)}$ = 1.80, \emph{P} = 0.037).}
Forecast error decreased significantly with the inclusion of climate
covariates for the \emph{B. gracilis} IPM (\(t_{(280)}\) = -3.72,
\emph{P} = \textcolor{blue}{0.01}) and QBM (\(t_{(280)}\) = -3.34,
\emph{P} \textless{} 0.0001), and for the \emph{Poa secunda} IPM
(\(t_{(196)}\) = -1.90, \emph{P} textcolor\{blue\}\{= 0.015\}) and QBM
(\(t_{(196)}\) = -2.47, \emph{P} = 0.007) (Fig. S1, Supporting
Information). In no case did including climate covariates significantly
decrease forecast skill (Table S21), despite small changes in the mean
skill (Fig. 2, \textcolor{blue}{Fig. S3}).

IPM forecasts were significantly more accurate than the QBM in only one
case (Fig. 2): forecast accuracy of \emph{P. smithii} percent cover from
an IPM with climate covariates was greater than the accuracy from the
QBM with climate covariates (\(t_{(215)}\) = 1.92, \emph{P} =
\textcolor{blue}{0.022}). However, adding climate covariates decreased
the skill of both models, and the difference between the IPM and QBM
emerges only because skill decreased less for the IPM than the QBM.
Results from all pairwise statistical tests are shown in Table S22 of
the Supporting Information.

With climate covariates included and using mean parameter values, the
accuracy of both models' forecasts declined as the distance between the
last observation and the forecast increased, but they did so at similar
rates (Fig. 4). The only exception is for \emph{Poa secunda}, where QBM
forecast accuracy remained steady as the temporal distance of the
forecast increased, whereas IPM forecast accuracy declined (Fig. 4). The
forecast horizons were short: forecast accuracy fell below \(\rho\) =
0.5 after one year for the IPM for most species, and after four years,
at most, for the QBM (Fig. 4). Across the different temporal distances
from the observation to the forecast, the IPM was never more accurate
than the QBM (\emph{P} \textgreater{} 0.05 for all one-sided
\emph{t}-tests, Table S23).
\textcolor{blue}{Likewise, the QBM was rarely more accurate the IPM, the only exceptions being for \emph{H. comata} at a temporal distance of three years ($t_{(98)}$ = 2.04, \emph{P} = 0.032) and \emph{B. gracilis} at a temporal distance of eight years ($t_{(37)}$ = 1.67, \emph{P} = 0.05) (Table S24).}
\st{There were some cases where the QBM was more accurate than the IPM for \emph{Poa secunda}, but neither model exceeded the forecast proficiency threshold by a large margin (Fig. 4, Table S24).}

@@

\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

@@
